A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-13 Paper/Manuscript.Rmd
Adjust caption size, software citation subfolder

@@

## Markdown (this is a 'level 2 heading')
Here are some examples of how to format text with Markdown.

@@

Here's how to **bold** or *italicize* a piece of text.

This is how you do a bullet point list:

@@

```{r include=FALSE}
cite_packages(out.format = "md", out.dir =  here("/Paper/SupplementaryMaterial"))

@@

```{r include = FALSE}
pkgs <- c("tidyverse", "here", "knitr", "stargazer", "ggpmisc", "gt", "grateful", "base", "rticles")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib", out.dir =  here("/Paper/SupplementaryMaterial") )
```

@@

# Results
Figure \@ref(fig:irises) shows petal widths by iris type.

@@

## Violin plot
Figure \@ref(fig:petalwidths) shows petal widths by iris type.

@@

# Acknowledgements
Don't forget to acknowledge the funder(s) with associated grant numbers if required. The same goes for folks who significantly assisted you with this paper but that are not authors. Eg "Agency (grant number 12345) supported this work, with cost share provided by the Center for the Built Environment. We thank Person1 and Person2 for assistance with data collection""

# Declaration of interest
Descibe any relevant interests of the authors, particularly if there is a link to the research that is relatively uncommon and could be perceived as a conflict of interest.  Otherwise, "All authors declare no conflict of interest."

>>>>

```{r figureFontSize, echo = FALSE}
# In the YAML header above, the font size for captions in this document is controlled by `[font={small}]` under `header-includes (note this is *larger* than the default size for this template*). For more options, see https://stackoverflow.com/questions/37136731/set-caption-font-size-for-figures-in-yaml-header-of-rmarkdown
```

@@

## Markdown (this is a 'level 2 heading')
This RMarkdown document is a special type of interactive document that can contain both code chunks (in R, python, or other languages), and text written in a format called Markdown. Here are some examples of how to format text with Markdown, and a [link](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf) to an RMarkdown guide.

@@

Here's how to **bold** or *italicize* a piece of text. This is how you do a bullet point list:

@@

```{r include=FALSE}
cite_packages(out.format = "md", out.dir =  here("/Paper/SupplementaryMaterial/Software_citations"), include.rmd = TRUE, all.pkg = TRUE)

@@

```{r include = FALSE}
pkgs <- c("tidyverse", "here", "knitr", "stargazer", "ggpmisc", "gt", "grateful", "base", "rticles")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib", out.dir =  here("/Paper/SupplementaryMaterial/Software_citations") )
```

@@

# Results
## Scatter plot example
Figure \@ref(fig:irises) shows petal widths by iris type.

@@

## Violin plot example
Figure \@ref(fig:petalwidths) shows petal widths by iris type.

@@

# Acknowledgements
Don't forget to acknowledge the funder(s) with associated grant numbers if required. The same goes for folks who significantly assisted you with this paper but that are not authors. Eg "Agency (grant number 12345) supported this work, with cost share provided by the Center for the Built Environment. We thank Person1 and Person2 for assistance with data collection"

# Declaration of interest
Descibe any relevant interests of the authors, particularly if there is a link to the research that is relatively uncommon and could be perceived as a conflict of interest.  Otherwise : All authors declare no conflict of interest.
